### 2012-09-01 inst/examples/figure3.Rmd
added coarse linear interp

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`

@@

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=16)
````

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e5)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r runall}
lvl <- 0.5
````

``` {r }
det <- scenario(0.0, 0.00, 0.00)
````

``` {r }
all_low <- scenario(0.1, 0.1, 0.1)
````

``` {r }
g   <- scenario(lvl, 0, 0)
````

``` {r }
m   <- scenario(0, lvl, 0)
````

``` {r }
i   <- scenario(0, 0, lvl)
````

``` {r }
gm  <- scenario(lvl, lvl, 0)
````

``` {r }
gi  <- scenario(lvl, 0, lvl)
````

``` {r }
mi  <- scenario(0, lvl, lvl)
````

``` {r }
gmi <- scenario(lvl, lvl, lvl)
````

```{r }
low <- all_low
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= i$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")
policy <- melt(data.frame(stock = x_grid, low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= i$D[,1]), 
               id = "stock")

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="figure3/", verbose=TRUE or`

@@

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=4)
````

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e3)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

``` {r runall}
lvl <- 0.5
det <- scenario(0.001, 0.00, 0.00)
g   <- scenario(lvl, 0, 0)
m   <- scenario(0, lvl, 0)
i   <- scenario(0, 0, lvl)
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= i$D[,1]), 
               id = "stock")
